A tutorial on Generalised Additive Mixed Effects Models for bilingualism research

### 2023-12-12 manuscript/manuscript.qmd
add authors

---
title: "A tutorial on Generalised Additive Mixed Effects Models for bilingualism research"
format: pdf
editor: visual
bibliography: gam_refs.bib
csl: apa.csl
---

>>>>

---
title: "A tutorial on Generalised Additive Mixed Effects Models for bilingualism research"
author: Stefano Coretta, Joseph V. Casillas
format: pdf
editor: visual
bibliography: gam_refs.bib
csl: apa.csl
---
